Phase paper outline your mom last night

### 2014-05-23 Manuscript/Phase_detectors_outline.tex
Added bibliography

\section*{Introduction}
\begin{itemize}
\item Physiological regulatory systems are reliably non-linear in their responses
\item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
\item Non-linearities and delays conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
\item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 
\item Phase information extracted from each oscillating system can provide information about the relationship between the two systems.
\item Phase is essentially how far along a cycle a particular oscillation is. 
\item The problem is that phase has been extracted by multiple different methods, and it is unclear whether there is a best option, or if specific methods are ideal for specific purposes.
\item Noise and time-variance present in physiological data makes this process more difficult.

>>>>

\section*{Introduction}
\begin{itemize}
\item Physiological regulatory systems are reliably non-linear in their responses
\item Signal transduction, be it physical signals like pressure or cellular signals like phosphorylation, introduces a delay between input and output. 
\item Non-linearities and delays \cite{ottesen_modelling_1997} conspire to generate oscillations in physiological control systems, for example oscillations in renal blood flow, or oscillations in cerebral blood flow.
\item Oscillating physiological systems can become synchronized if they are somehow physically coupled. For example, sinus arrhythmia caused by respiration. 
\item Phase information extracted from each oscillating system can provide information about the relationship between the two systems.
\item Phase is essentially how far along a cycle a particular oscillation is. 
\item The problem is that phase has been extracted by multiple different methods, and it is unclear whether there is a best option, or if specific methods are ideal for specific purposes.
\item Noise and time-variance present in physiological data makes this process more difficult.
